### 2022-06-13 manuscript/hiv-gwas.tex
Update on Overleaf.

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=\linewidth]{figures/example_simulation_trait_values}
		\caption{Example simulated data from two evolutionary scenarios where a phylogenetic correction to trait values improves GWAS power (right side) and where it does not (left side). These examples correspond to the empty points in Figure \ref{fig:simulationResults}. (A) and (B) show simulated pathogen trait values for a sub-clade of the 500-tip phylogeny with either (A) pathogen heritability of 15\% or (B) 65\%. Pathogen trait values at clustered tips are (A) less or (B) more correlated, depending on the heritability. (C) shows that our method produces corrected trait values (y-axis) that better match the true simulated host part of the trait (x-axis) when pathogen heritability is high (right side). Selection strength was fixed to 5 time $^{-1}$ for both scenarios and all other parameters were fixed as in the full simulation study.}
		\label{fig:simulationTraitExample}
	\end{center}
\end{figure}

>>>>

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=\linewidth]{figures/example_simulation_trait_values}
		\caption{Simulated data from two evolutionary scenarios where a phylogenetic correction to trait values improves GWAS power (right side) and where it does not (left side). These examples correspond to the empty points in Figure \ref{fig:simulationResults}. (A) and (B) show total trait values for 12 randomly selected tips from the simulated phylogeny with pathogen heritability 15 and 75\%, respectively. Depending on the pathogen heritability, trait values are more or less correlated at clustered tips. (C) compares our method's estimate for the non-pathogen part of trait values (y-axis) with true simulated host trait values (x-axis) with pathogen heritability 15 and 75\%. The solid line is the y=x line. Selection strength was fixed to 0.1 time $^{-1}$ for both scenarios and all other parameters were fixed as in the full simulation study.}
		\label{fig:simulationTraitExample}
	\end{center}
\end{figure}
